\resheading{Activities}
  \begin{itemize}[leftmargin=*]
  	\item\ressubheading{I-VISTA Challenge}{2018.08 -- 2018.09}{Team Member}{Chongqing, China}{\small
  		\begin{itemize}
  			\item {It is a competition of autonomous driving held in Chongqing, China. It includes five subs: Automatic Parking (AP), Automatic Emergency Brake (AEB), Innovation Application (IA), Commercialization Process (CP), and Urban Traffic (UT).}
  			\item {I was a team member of the Sun Yat-sen University team. My Team participated in AEB, IA, CP, and UT. And we were ranked medium among 20+ teams finally.}
  		\end{itemize}}
  	
  	
    \item\ressubheading{PACE Center of Tongji University}{2014.09 -- 2017.09}{Student Leader}{Shanghai, China}
    {\small\begin{itemize}
        \item {TJU PACE is an organization held by both Tongji University and PACE (https://pacepartners.org/).}
        \item {As a project leader, I was in collaboration with more than 30 students from the Polytechnic of Turin (UNITO) and Korea National University (Kookmin University), before and after, participated in two international cooperation projects: the RSMS (2016) and PUMA (2017). Both projects are competition projects, RSMS is a project to design and engineer a theoretically producible reconfigurable shared-use vehicle based on current or emerging technology, and PUMA requires teams to create a vehicle for commuting in a city that is buildable and theoretically producible for mass-production using current technology. RSMS project results in 2016, the annual global conference of the PACE in USA acclaim. PUMA project results obtained in 2017 annual global conference of PACE, the first prize of the overall project, the industrial design, and manufacturing engineering.}
        \item {As a project director, I guide the independent research and development project of Tongji PACE which called Smart Express System (IDS). The project won the first prize and the sixteenth Chen Geng Qing Shanghai Young Inventors Awards prize in 2017 CIC PACE global competition.}
        \item{I also create a unique project management tool called KRRS for Tongji PACE center, to quantify the progress of the project and members' contribution to the project.}
	    \end{itemize}}
	    
  \end{itemize}