\resheading{Research}
  \begin{itemize}[leftmargin=*]
    \item \ressubsingleline{Motion Planning for Autonomous Driving}{}{2018.09 -- Now}{\small
    	\begin{itemize}
    		\item{My research topic during the Master period is motion planning for autonomous driving. I focus on the
         	fusion of traditional methods and deep learning methods. Specifically, I work on using the deep
         	convolutional neural networks (YOLO, R-CNN, etc.) to provide a more effective heuristic for
         	sampling-based planning methods (RRT*, Bi-RRT*, etc.).}
		    \item{From Sep. 2018 to May 2019, I had proposed a method: using CNNs to generate a more applicable
         	sampling heuristic for RRT* used for autonomous cruising. The work derived an invention patent.}
	        \item{From May 2019 to Now, I am working on path planning for autonomous parking. I propose a two-stages method using firstly CNNs to infer a path directly and then RRT*-based algorithms to guarantee the path is feasible. A paper of that work is reviewed by the ICAPS conference now.}
         \end{itemize}}
    
    \item \ressubsingleline{Tongji students innovative training program}{}{2016.09 -- 2017.09}{\small
    	\begin{itemize}
    		\item{This is a project launched by Tongji University for training students on researching. I explored a new suspension system for small electric vehicles based on the in-wheel motor technology, The proposal passed the evaluation held by the university.}
    	\end{itemize}}

  \end{itemize}
